Are kelp forests different? A comparison of kelp forests between contrasting study sites

### 2018-07-16 paper_draft.Rmd
edit...

plot_flora <- ggplot(data = flora_lng, aes(x = species, y= biomass, fill = site)) + 
              geom_bar(stat = "identity", show.legend = FALSE, position=position_dodge()) + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'grey', colour = 'black')) +
              ylab("Flora") + 
              xlab("") +
              coord_flip()
```

Diveristy of fauna was...

@@

plot_fauna <- ggplot(data = fauna_lng, aes(x = species, y= biomass, fill = site)) + 
              geom_bar(stat = "identity", show.legend = FALSE ,position=position_dodge(),
              size=.3) + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'grey', colour = 'black')) +
              ylab("Fauna") + 
              xlab("") +
              coord_flip()
```

```{r biomass barplot, message=FALSE, warning=FALSE, paged.print=FALSE}
ggarrange(plot_flora, plot_fauna)
```

>>>>

plot_flora <- ggplot(data = flora_lng, aes(x = species, y= biomass, fill = site)) + 
              geom_bar(stat = "identity", show.legend = FALSE, position=position_dodge()) + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'white', colour = 'white')) +
              ylab("") + 
              xlab("") +
              coord_flip()
```

Diveristy of fauna was.....

@@

plot_fauna <- ggplot(data = fauna_lng, aes(x = species, y= biomass, fill = site)) + 
              geom_bar(stat = "identity", show.legend = TRUE ,position=position_dodge(),
              size=.3) + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'white', colour = 'white')) +
              ylab("") + 
              xlab("") +
              coord_flip()
```

```{r biomass barplot, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap='Comparison of raw biomass species data between sites. Graph A represents flora and graph B represents fauna.'}
ggarrange(plot_flora, plot_fauna, ncol = 2, nrow = 1, labels = "AUTO", legend = "bottom", common.legend = TRUE)
```
